---
title: "PSTAT 5LS Lab 5"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pstat5lsSBI)
```

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

# Lab Tutorial

```{r tryit1, error = T}
# Run this chunk to have R show you a visualization for the p-value for the lemur example. Be sure to run the setup chunk above first.
plot_t(3.722, df = 53, 
       shadeValues = c(-3.722, 3.722), 
       direction = "beyond")

```

```{r tryit2, error = T}
# Make sure to enter the value of the test statistic and the degrees of freedom below before running it to calculate the p-value for the lemur example.
2*pt(q =  , df =  , lower.tail = FALSE)

```

```{r loadPenguins, error = T}
penguins <- read.csv("penguins.csv", stringsAsFactors = TRUE)

```

```{r tryit3, error = T}
# Run the following chunk to create a histogram of the flipper lengths 
hist(penguins$flipper_length_mm,
     main = "Histogram of Flipper Length",
     xlab = "Flipper length (mm)",
     col = "#09847A")

```

```{r gentoo_subset, error = T}
gentoo <- subset(penguins, penguins$species == "Gentoo")

```

```{r tryit4, error = T}
# Like before, be sure to specify the variable that you want to make a histogram of below. Remember that now the data set we want the data set with only the Gentoo penguins.
hist( ,
     main = "Histogram of Flipper Length for Gentoo Penguins",
     xlab = "Flipper length (mm)",
     col = "#09847A")

```

```{r tryit5, error = T}
# Make sure to specify the hypothesized mean in the `mu` argument and the alternative in the `alternative` argument ("two.sided", "less", "greater")
t.test(gentoo$flipper_length_mm, 
       mu =   , 
       alternative =  )

```

```{r tryit6, error = T}
# Run this code chunk to have R produce summary statistics for the mean flipper length of Gentoo penguins
summary(gentoo$flipper_length_mm)
sd(gentoo$flipper_length_mm)

```

```{r tryit7, error = T}
# Enter values for `p`, `df`, and `lower.tail` below and then run this chunk to get the critical value
qt(p =  , df =  , lower.tail =  )

```

```{r tryit8, error = T}
# Specify the value for `conf.level` and then run this chunk to have R produce a 95% confidence interval for the mean flipper length of Gentoo penguins
t.test(gentoo$flipper_length_mm, conf.level = )

```

# Symbol Cheat Sheet

Inequality

$\neq 0$

Population means:

$\mu$

$\mu_d$

$\mu_1 - \mu_2$

$\mu_1$

$\mu_2$

Sample means:

$\bar{x}$

$\bar{x}_d$

$\bar{x}_1 - \bar{x}_2$

$\bar{x}_1$

$\bar{x}_2$

Curious to learn more about formatting math in RMarkdown? More or less, RMarkdown and Knitr use LaTeX formatting (pronounced "LAY-tech" or "LAH-tech") to produce math characters and expression, so most guides you read on typesetting math in LaTeX will also apply to Rmd. If you're interested (and to be clear, this is not required for any part of the course), I'd check out [this tutorial from Overleaf](https://www.overleaf.com/learn/latex/Mathematical_expressions) first. And here is a [pretty extensive cheatsheet for symbols](https://www.caam.rice.edu/~heinken/latex/symbols.pdf). 

# Code Cheat Sheet

## `pt(q, df, lower.tail = TRUE)`

- `q` is the x-axis value you want to find an area related to
- `df` is the degrees of freedom of the $t$ distribution
- `lower.tail` determines whether `pt()` finds the area to the left or right of `q`. If `lower.tail = TRUE` (the default), it shades to the left. If `lower.tail = FALSE`, it shades to the right.
  
## `qt(q, df, lower.tail = TRUE)`

- `p` is the probability or area under the curve you want to find an x-axis value for
- `df` is the degrees of freedom of the $t$ distribution
- `lower.tail` determines whether `pt()` finds the area to the left or right of `q`. If `lower.tail = TRUE` (the default), it shades to the left. If `lower.tail = FALSE`, it shades to the right.
  
## `plot_t()`

- `df` refers to the degrees of freedom of the distribution to plot. You must provide this value.
- `shadeValues` is a vector of up to 2 numbers that define the region you want to shade
- `direction` can be one of `less`, `greater`, `beyond`, or `between`, and controls the direction of shading between `shadeValues`. Must be `less` or `greater` if `shadeValues` has only one element; `beyond` or `between` if two
- `col.shade` controls the color of the shaded region, defaults to `"cornflowerblue"`
- `...` lets you specify other graphical parameters to control the appearance of the normal curve (e.g., `lwd`, `lty`, `col`, etc.)

## `t.test(x, alternative, mu, conf.level)`
- `x` is a vector of data values
- `alternative` specifies the direction of the alternative hypothesis; must be one of "two.sided", "less", or "greater"
- `mu` indicates the true value of the mean (under the null hypothesis); defaults to 0
- `conf.level` is the confidence level to be used in constructing a confidence interval; must be between 0 and 1, defaults to 0.95

## Important plotting arguments

### `main = "Title of Your Graph in Double Quotes"`

- graph title that must be inside a set of double quotes

### `xlab = "x-axis Label of Your Graph in Double Quotes"`

- the x- (horizontal) axis label that must be inside a set of double quotes

### `ylab = "y-axis Label of Your Graph in Double Quotes"`

- the y- (vertical) axis label that must be inside a set of double quotes
