---
title: "PSTAT 5LS Lab 3 Notes"
author: "Your Name Here"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pstat5lsSBI)
```

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

```{r tryIt1, error = T}
# Run this code chunk to have R plot what the proportion of AP Statistics test scores less than 2 looks like
plot_norm(mean = 2.85, 
          sd = 0.43, 
          shadeValues = 2, 
          direction = "less", 
          col.shade = "cornflowerblue")
```

```{r tryIt2, error = T}
# Fill in the values for `q`, `mean`, `sd`, and `lower.tail` below to calculate the proportion of AP Statistics test scores less than 2. Then run this code chunk
pnorm(q = , 
      mean = , 
      sd = , 
      lower.tail = )
```

```{r tryIt3, error = T}
# Run this code chunk to have R plot the proportion of AP Statistics test scores that are between 3 and 3.5
plot_norm(mean = 2.85, 
          sd = 0.43, 
          shadeValues = c(3, 3.5), 
          direction = "between", 
          col.shade = "cornflowerblue")
```

```{r tryIt4, error = T}
# Below is the code you need to calculate the area between 3 and 3.5 for the AP Statistics test scores. Run this chunk to find this area
pnorm(c(3, 3.5), 
      mean = 2.85, 
      sd = 0.43, 
      lower.tail = TRUE) 

```

```{r, tryIt5, error = T}
# Below is the code that would return the proportion of AP Statistics scores to the left of 3.0. Make the change so that R returns the proportion to the RIGHT of 3
pnorm(q = 3, 
      mean = 2.85, 
      sd = 0.43, 
      lower.tail = TRUE)

```

```{r, tryIt6, error = T}
# Fill in the values for `p` and `lower.tail` to find the score an AP Statistics student needs to be in the top 10% and then run this chunk 
qnorm(p = , 
      mean = 2.85, 
      sd = 0.43, 
      lower.tail = )

```

# Code Cheat Sheet

## `plot_norm()` 

- `mean`: the mean of the normal distribution you'd like to draw ($\mu$)
- `sd`: the standard deviation or standard error of the normal distribution you'd like to draw ($\sigma$ or $\sqrt{\frac{p_0(1-p_0)}{n}}$, respectively)
- `shadeValues` (optional): either a number or a vector of two numbers (using `c()`) that are the boundaries of the region you'd like to shade.
- `direction`: where to shade (`"less"`, `"greater"`, `"between"`, or `"beyond"`)
- `col.shade`: the color to use when shading
- any other graphical parameters you want to use to control the appearance of the plot (like `main`, etc.)

## `pnorm(q, mean, sd, lower.tail = TRUE)`

- `q`: the x-axis value you want to find an area related to
- `mean`: the mean of the normal distribution, defaults to 0
- `sd`: the standard deviation of the normal distribution, defaults to 1
- `lower.tail` determines whether `pnorm()` finds the area to the left or right of `q`. If `lower.tail` is set to \textcolor{blue}{`TRUE`} (the default), it finds the probability to the \textcolor{blue}{LEFT}. If `lower.tail` is set to \textcolor{red}{`FALSE`}, it finds the probability to the \textcolor{red}{RIGHT}.

## `qnorm(p, mean, sd, lower.tail = TRUE)`

- `p`: the probability or area under the curve you want to find an x-axis value for
- `mean`: the mean of the normal distribution, defaults to 0
- `sd`: the standard deviation of the normal distribution, defaults to 1
- `lower.tail`: determines whether `qnorm()` finds the value of the variable with area `p` to its left or right. If `lower.tail` is set to \textcolor{blue}{`TRUE`} (the default), the area `p` is to the \textcolor{blue}{LEFT}. If `lower.tail` is set to \textcolor{red}{`FALSE`}, the area `p` is to the \textcolor{red}{RIGHT}.

## Important plotting arguments

### `main = "Title of Your Graph in Double Quotes"`
- graph title that must be inside a set of double quotes

### `xlab = "x-axis Label of Your Graph in Double Quotes"`
- the x- (horizontal) axis label that must be inside a set of double quotes

### `ylab = "y-axis Label of Your Graph in Double Quotes"`
- the y- (vertical) axis label that must be inside a set of double quotes