---
title: "PSTAT 5LS Lab 2 Notes"
author: "Your Name Here"
date: "Winter 2026"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats250sbi)
```

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

# Lab Code

Use the chunks below to try out any code that you'd like. 

## Setting a Seed

Run the `setSeed` code chunk below. No output will occur, but it will set the seed so that we all get the same results. 

```{r setSeed, error = T}
set.seed(2573)
```

We chose the number 2573 arbitrarily.

If you execute the code chunk that contains the `set.seed()` code again, it will start your random number generator at the beginning of the sequence.

When you knit your document, it will also start your random number generator at the beginning of the sequence.

## `simulate_chance_model()`

In order to understand our new function, let's utilize the help feature.

```{r aboutSimulate, error = T}
# Run this code chunk to generate the help feature for the `simulate_chance_model()` function
?simulate_chance_model

```

## Simulation Example

Lee is a teacher at a local high school who wanted to assess whether or not dogs physically resemble their owners enough for people to be able to correctly match a dog to their owner better than if just guessing. Lee, who is also a dog owner, showed pictures of four dogs to her class of 40 students. One photo was of the teacher's dog (Yoda) and the other three photos were of dogs belonging to Lee's friends. The students were asked to guess which dog was actually the teacher's. If dogs do not physically resemble their owners, the students would get a correct match 25\% of the time, since the students would be equally likely to choose any of the four dogs. It turned out that 17 of the 40 students correctly picked out the teacher's dog.

## Sample Proportion

Use R to calculate the proportion of students who correctly picked out the teacher's dog.

```{r sampProp, error = T}
# Replace "number of successes" and "sample size" in the code block below and then run this chunk to calculate the sample proportion 

phat <- (number of successes)/(sample size)
phat

```


## Hypotheses

What are the hypotheses to be tested? State the hypotheses using symbols. Be sure to define the parameter. You'll want to define both $H_0$ and $H_A$.

$H_0$: *Write your answer here*

$H_A$: *Write your answer here*

where *write your symbol here* represents the *write your answer here*.

## Setting Up the Simulation
|                   | **Assuming the chance model...** |
|-------------------|----------------------------------|
| One draw          | *Write your answer here*         |
| Blue poker chip   | *Write your answer here*         |
| Yellow poker chip | *Write your answer here*         |
| Chance of blue    | *Write your answer here*         |
| One repetition    | *Write your answer here*         |

## Code to Simulate

In the `runSim` code chunk below, add the values for `chanceSuccess`, `numDraws`, and `numRepetitions` to run the simulation 1000 times. Then run the chunk.

```{r runSim, error = T}
# Run this code chunk to run the simulation, and assign it to the name sim1
sim1 <- simulate_chance_model(chanceSuccess = , 
                              numDraws = , 
                              numRepetitions = )

```

`sim1` should now be in your environment in the top right corner.

Notice that the first time you run this code, you get the **exact same values** we got! This is because we both set the same seed! If you run the code again, your values will change. The number of times that you run your code dictates where your random number generator is in the sequence of random numbers.

## Making a Visualization of the Simulation Results

Run the following code chunk to make a histogram of the simulation results.

```{r simHist, error = T}
# Run this code chunk to create a histogram of the simulated proportions, and include a red vertical line at the value of the observed sample proportion
hist(sim1, 
     main = "Histogram of 1000 Simulation Results",
     xlab = "Simulated Proportion of Correct Guesses",
     xlim = c(0, 1))
abline(v = 17/40, col = "red")
```

## Code to Find the Estimated p-value

Enter the code to calculate the estimated p-value and then run this chunk.

```{r estpvalue, error = T}
# Run this code chunk to find the probability of getting the sampled results or more extreme

```

## Conclusion

What do the results tell us about our research question?

Do we have enough evidence to support the claim that dogs physically resemble their owners enough for people to be able to correctly match a dog to their owner **better** than if just guessing?

*Write your answer here*

# Code Cheat Sheet

## `set.seed(seed)`
Sets the "seed" of R's random number generator. After setting the seed, the sequence of random numbers R will produce is entirely determined/predictable. This is useful for ensuring you get the same results whenever you knit your code.

- `seed` is an integer. The seed you want to set.

## `simulate_chance_model(chanceSuccess, numDraws, numRepetitions)`
- `chanceSuccess`: a number between 0 and 1 represending the probability of observing a "success"
- `numDraws`: the number of times to draw a poker chip from the bag needed to complete one repetition of the simulation
- `numRepetitions`: the number of times to repeat the simulation process

## `abline(linear_model_name)`
- Will plot the line found in `linear_model_name`
- Use `v = value` to print a vertical line

## Important plotting arguments

### `main = "Title of Your Graph in Double Quotes"`
- graph title that must be inside a set of double quotes

### `xlab = "x-axis Label of Your Graph in Double Quotes"`
- the x- (horizontal) axis label that must be inside a set of double quotes

### `ylab = "y-axis Label of Your Graph in Double Quotes"`
- the y- (vertical) axis label that must be inside a set of double quotes

# Installing the `stats250sbi` package 

1. Open up RStudio in JupyterHub and open the Console.
2. In the Console, type in this code: `install.packages(c("remotes", "checkmate"))`. Let R install these two packages. 
3. Once R has installed the `remotes` and `checkmate` package, you can type in this code in the Console:  `remotes::install_github("STATS250SBI/stats250sbi", dependencies = TRUE)`. Let R install this package.
4. Once R has installed the `stats250sbi` package, you can now run this R code: `library(stats250sbi)`. If creating an RMarkdown file, this code will need to be in one of the first chunks of your document. 
