---
title: "PSTAT 5LS Lab 4 Notes"
author: "Your Name Here"
output: html_document
header-includes:
  - \renewcommand{\footnotesize}{\tiny}
  - \newcommand{\theHtable}{\thetable}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pstat5lsSBI)
```

# Lab Notes

Use this place to take any notes during your lab section.

- Type any notes here
- Add new notes by using the dash `-` to create a list

# Lab Tutorial

```{r tryIt1, error = T}
# Run this chunk to visualize the estimated p-value
SE <- round(sqrt(0.70 * (1 - 0.70) / 750),4)

plot_norm(mean = 0.70, 
          sd = SE, 
          shadeValues = c(0.672, 0.728), 
          direction = "beyond", 
          col.shade = "darkgreen")
```

```{r tryIt2, error = T}
# Run this chunk to get an estimated p-value using the normal distribution
2 * pnorm(q = 0.672, mean = 0.70, sd = 0.0167, lower.tail = TRUE)
```

```{r tryIt3, error = T}
# Enter the number of successes (x), sample size (n), hypothesize proportion (p), and alternative ("less", "greater", "two-sided") below and then run this chunk to calculate the test statistic and the p-value
prop_test(x = , 
          n = , 
          p = , 
          alternative = )

```

```{r, tryIt4, error = T}
# Enter values for `x`, `n`, and `conf.level` below and then run this code chunk to calculate a 98% confidence interval
prop_test(x = , 
          n = , 
          conf.level = )
```

# Code Cheat Sheet

## `set.seed(seed)`
Sets the "seed" of R's random number generator. After setting the seed, the sequence of random numbers R will produce is entirely determined/predictable. This is useful for ensuring you get the same results whenever you knit your code.

- `seed` is an integer. The seed you want to set.

## `simulate_chance_model(chanceSuccess, numDraws, numRepetitions)`

- `chanceSuccess`: a number between 0 and 1 represending the probability of observing a "success"
- `numDraws`: the number of times to draw a poker chip from the bag needed to coplete one repetition of the simulation
- `numRepetitions`: the number of times to repeat the simulation process

## `abline(linear_model_name)`

- Will plot the line found in `linear_model_name`
- Use `v = value` to print a vertical line

## `plot_norm()` 

- `mean`: the mean of the normal distribution you'd like to draw ($\mu$)
- `sd`: the standard deviation or standard error of the normal distribution you'd like to draw ($\sigma$ or $\sqrt{\frac{p_0(1-p_0)}{n}}$, respectively)
- `shadeValues` (optional): either a number or a vector of two numbers (using `c()`) that are the boundaries of the region you'd like to shade.
- `direction`: where to shade (`"less"`, `"greater"`, `"between"`, or `"beyond"`)
- `col.shade`: the color to use when shading
- any other graphical parameters you want to use to control the appearance of the plot (like `main`, etc.)

## `prop_test(x, n, p, alternative)`

- `x`: the number of successes observed in the study
- `n`: the sample size of the study
- `p`: the value of the null hypothesis
- `alternative`: the direction of the alternative hypothesis; choices are `"two.sided"` (default), `"greater"`, or `"less"`

## `pnorm(q, mean, sd, lower.tail = TRUE)`

- `q`: the x-axis value you want to find an area related to
- `mean`: the mean of the normal distribution, defaults to 0
- `sd`: the standard deviation of the normal distribution, defaults to 1
- `lower.tail` determines whether `pnorm()` finds the area to the left or right of `q`. If `lower.tail` is set to \textcolor{blue}{`TRUE`} (the default), it shades to the \textcolor{blue}{LEFT} If `lower.tail` is set to \textcolor{red}{`FALSE`}, it shades to the \textcolor{red}{RIGHT}.

## Important plotting arguments

### `main = "Title of Your Graph in Double Quotes"`
- graph title that must be inside a set of double quotes

### `xlab = "x-axis Label of Your Graph in Double Quotes"`
- the x- (horizontal) axis label that must be inside a set of double quotes

### `ylab = "y-axis Label of Your Graph in Double Quotes"`
- the y- (vertical) axis label that must be inside a set of double quotes
